
This is template for thesis. I created it for my own need when I had to write PhD confirmation thesis and searched for some default Massey \LaTeX template. To my surprise I have found that Massey do not support any \LaTeX template and even their instruction for how should thesis be written are sparse and weird. So I decided to improve life of other people that come after me and created this template. If you are experienced user, you might use it as starting point, it is your work and \LaTeX enables great deal of personalization, so feel free to modify it, improve it and so on. If you are starting user of \LaTeX, you might be grateful for a working template that looks good, is not overcombined with fancy stuff and provide good basic settings, from page layout (notably reduction of empty space), a good citation style for bibtex (APA is best) and decent titlepage.

\section{Knitr or not knitr?}
Previous version of this template (and my confirmation report) was based on knitr and associated \code{.rtex} files. Knitr is an \code{R} package that compile \code{.rtex} files, evaluate any \code{R} snippets included in them and outputs \code{.tex} file with evaluated snippets, these could be \code{R} commands and their output or even figures and tables build directly from data! Knitr is a great tool, however as my confirmation report grew bigger and more complex, it became harder to build everything from scratch with knitr. Figures build from data took very long to produce, with a more complex table design it was harder and harder to produce them with \code{xtable} package (I had to do quite a lot of hack to make it right) and the compilation time grew so much that I was able to go get coffee in the meantime. And if you wanted to manually edit and fix something, you couldn't.

So instead of knitr, I generated all my tables and all my figures separately, did as much as I could to make them look good with R/python/tikZ and then manually edited them (e.g., with inkscape) to get the best final look.
